Toward dynamic models of combat or lack thereof in animal mating

### 2016-03-15 ms.tex
clustering plots, ms changes

\newcommand{\myfigure}[4]{
\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=9cm,keepaspectratio]{#1}
    \caption{#2}
    \centering
    \includegraphics[width=10cm,height=9cm,keepaspectratio]{#3}
    \caption{#4}
\end{figure}
}

@@

Within the immature phase, we assume males grow with rate
\begin{equation} \label{eq:growth}
    \frac{dm}{dt} = a m^ b
\end{equation}

@@

@@

If we assume a constant mortality rate $k_{im}$ during the immature phase, the probability of a male surviving to time $t$ from $0$ is given by
\begin{equation} \label{eq:surv_immature}
    S(t) = \exp(-k_{im} t).
\end{equation}

When a male matures it is given an energy budget linearly proportional to its mass such that: 
$$ E = k_em$$
After a male matures it cannot gain more energy.

@@

The area that a male with speed trait $v$ and radius trait $r$ can search in one time step is
\begin{equation}
    2 \cdot r \cdot v
\end{equation}
See Fig. \ref{fig:area searched}.

We let the total area enclosing all males and all nests be a parameter, $A_{total}$. We assume spatially random nests.

The encounter rate $\varepsilon$ for an individual is:
\begin{equation} \label{eq:encounter rate}
    \varepsilon = \frac {N \cdot 2 \cdot r \cdot v} {A_{total}}
\end{equation}
\citep{Gurarie2012}

We then use this as the rate parameter $lambda$ to repeatedly draw the time of the next event for this individual from the exponential distribution, we do this for each male from when they mature up to when the females mature.
When an event occurs we select a nest randomly and then the male will either occupy the nest or contest another male for control of the nest.

@@

The energy used by a mature male male with speed $v$ and radius $r$ is 
\begin{equation}
    E(r,v) = k_{search} \cdot r \cdot v
\end{equation}
where $k_{search}$ is a constant.

@@

\subsection{Contest Algorithm}
Contests 
When a searching male encounters a nest that is occupied a contest over possession of that nest occurs. Contests occur instantaneously.

@@

$$Energy Spent = \int_0^{c_i}{\kappa(t)}dt$$

if the $\kappa$ is $commitment^2$ then
$$EnergySpent = \frac{c_i^3}{3}$$
Where $c_i$ is the losing male.

The male chooses how much energy to commit based off of a commitment function, we examine two different commitment functions, for a male $i$ against a male $j$

@@

%And a linear one:
% $$\mathrm{commitment} = \beta + \alpha \cdot (\frac{m_i - m_j}{m_i + m_j})$$

@@

\myfigure{figures/energy_pc_plot_cm_100.pdf}{pc energy spent on what}{figures/energy_total_plot_cm_100.pdf}{total energy spent on what}

\myfigure{figures/e_0_nest_density.pdf}{e 0 with patch area}{figures/k_patch_area.pdf}{k with patch area}

\myfigure{figures/e_0_nest_density.pdf}{e 0 with nest density}{figures/k_patch_area.pdf}{k with nest density}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm,keepaspectratio]{figures/cm_100_num_winners.pdf}
    \caption{Number of successful males at different patch areas}
\end{figure}

>>>>

\newcommand{\myfigure}[4]{
\begin{figure}[h!]
    \centering
    \includegraphics[width=13cm,height=10cm]{#1}
    \caption{#2}
    \centering
    \includegraphics[width=13cm,height=10cm]{#3}
    \caption{#4}
\end{figure}
}

@@

% whats b? define/ state value
Within the immature phase, we assume males grow with rate
\begin{equation} \label{eq:growth}
    \frac{dm}{dt} = a m^ b
\end{equation}

@@

% needs more detail, need location and width parameter values

@@

% state k_im value and example probability
If we assume a constant mortality rate $k_{im}$ during the immature phase, the probability of a male surviving to time $t$ from $0$ is given by
\begin{equation} \label{eq:surv_immature}
    S(t) = \exp(-k_{im} t).
\end{equation}

When a male matures it is given an energy budget linearly proportional to its mass such that: 
$$ E = k_em$$
After a male matures it cannot gain more energy. When a mature male uses its energy allocation it dies.

@@

The area that a male with speed trait $v$ and radius trait $r$ can search in one time step is
\begin{equation}
    2 \cdot r \cdot v
\end{equation}
A male is 
See Fig. \ref{fig:area searched}.

The energy used by a searching male with speed $v$ and radius $r$ is 
\begin{equation}
    E(r,v) = k_{search} \cdot r \cdot v
\end{equation}
where $k_{search}$ is a constant.  % state value

We let the total area enclosing all nests be a parameter, $A_{total}$.
$N$ is the number of nests enclosed. $\frac{N}{A_{total}}$ is the nest density.

The encounter rate $\lambda$ for an individual is:
\begin{equation} \label{eq:encounter rate}
    \lambda = \frac {N \cdot 2 \cdot r \cdot v} {A_{total}}
\end{equation}
\citep{Gurarie2012}
We assume spatially random nests so nest discovery is a poisson process with the the expected number of encounters in one time step being $\lambda$.
Because of this we can then use this as the rate parameter to repeatedly draw the time of the next event for this individual from the exponential distribution.
We do this for each male from when they mature up to when the females mature.
When an event occurs we select a nest randomly and then the male will either occupy the nest or contest another male for control of the nest.

@@

@@

\subsection{Contests}
When a searching male encounters a nest that is occupied a contest over possession of that nest occurs. Contests occur instantaneously, taking up .

@@

$$Energy Spent = \int_0^{c_i}{\kappa(t)}dt $$

if the $\kappa(c)$ is $c^2$ then
$$EnergySpent = \frac{c_i^3}{3}$$
Where $c_i$ is the losing male.

The male chooses how much energy to commit based off of a commitment function. for a male $i$ against a male $j$

@@

@@

\myfigure{figures/energy_pc_plot_cm_100.png}{pc energy spent on what}{figures/energy_total_plot_cm_100.png}{total energy spent on what}

\myfigure{figures/e_0_patch_area.png}{e 0 with patch area}{figures/clustered_e_0_plot.pdf}{an equivilant plot with k means clustering done, with the k parameter chosen by $pamk$, the number of clusters (coexisting strategies) can be be seen on the left}
